Paper Results Section

### 2020-01-24 notebooks/old_notebooks/paper_L123_results_section.Rmd
updated notebooks (by moving old ones into subdir), added new one, new code

# TODO: error -> ?
los <- lapply(los, function(lofun) lapply(lofun, map_error_to_any))
```

@@

DEBUG: Classes
```{r}
L0_poly_class_args <- reduce_extracted_lopkgs_to_one(apply_extract_to_lopkg(los, extract_poly_class_args))
L0_poly_class_args <- L0_poly_class_args[order(-L0_poly_class_args$count),] # sort by count
L0_poly_class_args$perc <- round(L0_poly_class_args$count/sum(L0_poly_class_args$count) * 100, 1)
```
```

>>>>

# error -> ?
los <- lapply(los, function(lofun) lapply(lofun, map_error_to_any))

# ?? Attribute name, type to name only
los <- lapply(los, function(lofun) lapply(lofun, attr_name_type_to_name_df))
```

@@

### 2020-01-24 notebooks/old_notebooks/paper_results_section.Rmd
updated notebooks (by moving old ones into subdir), added new one, new code

# There's at least one transformation that we're always gonna want to apply, namly the vector/scalar
# collapse where both are present in a signature.
los <- lapply(los, function(lofuns) {lapply(lofuns, combine_scalar_vector_where_appropriate)})
# Figure out which ones are matrices. Remove if the analysis picks this up (and we rerun).
los <- lapply(los, function(lofun) lapply(lofun, distinguish_matrices_df))
```

@@

Now, having noted that:
(1) ints and doubles are basically interchangable, and
(2) null and NA should be a part of every type,
while also noting that together these make up a huge portion of the polymorphism, we transform.
```{r}
los <- lapply(los, function(s) lapply(s, fold_NULL_and_NA_into_other_types_df))
null_na_fold_arg_counts <- build_arg_count_df_from_lopkgs(los)
null_na_fold_fun_counts <- build_fun_count_df_from_lopkgs(los)

@@

@@

top_10_big_df %>% xtable

@@

>>>>

# There's at least one transformation that we're always gonna want to apply, namly the vector/scalar
# collapse where both are present in a signature.
los <- lapply(los, function(lofuns) {lapply(lofuns, combine_scalar_vector_where_appropriate)})
# Figure out which ones are matrices. Remove if the analysis picks this up (and we rerun).
los <- lapply(los, function(lofun) lapply(lofun, distinguish_matrices_df))
# remove "errors"
los <- lapply(los, function(lofun) lapply(lofun, remove_err_df))
```

@@

Now, having noted that:
(1) ints and doubles are basically interchangable, and
(2) null and NA should be a part of every type,
while also noting that together these make up a huge portion of the polymorphism, we transform.
```{r}
los <- lapply(los, function(s) lapply(s, fold_NULL_and_NA_into_other_types_df))
# null_na_fold_arg_counts <- build_arg_count_df_from_lopkgs(los)
# null_na_fold_fun_counts <- build_fun_count_df_from_lopkgs(los)

@@

Coindcidence stuff.
```{r}
index_list_coincide <- get_fun_sigs_matching_pred_from_lopkg(los, does_df_have_coinciding_types_index_and_list_or_vector)

# how many index-y things are there in here?
poly_type_args_i <- reduce_extracted_lopkgs_to_one(apply_extract_to_lopkg(list(index_list_coincide), extract_poly_type_args))
poly_type_args_i <- poly_type_args_i[order(-poly_type_args_i$count),] # sort by count

# in the reduced one:
sum_indexy_in_lopoly(poly_type_args_i)

# in full poly:
sum_indexy_in_lopoly(poly_type_args)

# perc
sum_indexy_in_lopoly(poly_type_args_i) / sum_indexy_in_lopoly(poly_type_args)
```

@@

top_10_big_df %>% xtable %>% print(include.rownames=F)

@@

Get biggest packages.
```{r}
packages_by_size <- get_biggest_packages(los, metric = size_of_signature_type)

top_10_size_df <- data.frame(
  pkg = names(packages_by_size[1:10]),
  size = packages_by_size[1:10]
)

rownames(top_10_size_df) <- NULL

top_10_size_df %>% xtable %>% print(include.rownames=F)
```
